Data Exploration

### 2018-11-27 src/data_exploration.Rmd
density plots + addition of tiff to gitignore

---
title: "Data Exploration"
author: "Samantha Andrews"
output: html_notebook
---

@@

@@

```{r}
pairs.panels(pres_env_cor)
```

>>>>

---
title: "Data Exploration"
author: "Samantha Andrews"
output: 
  html_notebook: 
    fig_height: 7
    fig_width: 10
editor_options: 
  chunk_output_type: inline
---

@@

to get some density plots all in one graphic, you need to change chunk output to in console, then go to the plot tab, make it fill the screen, then run then make bigger then save :( (probably a better way - this seems to be an issue with RStudio)
```{r}
par(mfrow=c(4,4))
for(i in 1:16){
  plot(density(background_env[,i], na.rm=T), main = names(background_env)[i])
}
```
PUT THE CHUNK OUTPUT BACK TO INLINE

@@

to get some density plots all in one graphic, you need to change chunk output to in console, then go to the plot tab, make it fill the screen, then run then make bigger then save :( (probably a better way - this seems to be an issue with RStudio)
```{r}
par(mfrow=c(4,4))
for(i in 1:16){
  plot(density(pres_env[,i], na.rm=T), main = names(pres_env)[i])
}
```
PUT THE CHUNK OUTPUT BACK TO INLINE
